---
title: "Template_Script_RMarkdown"
author: "Esther Cros"
output: html_document
date: "2025-01-14"
---

## Introduction

In this example, we'll explain how to structure and comment R code to make it more readable and understandable by other scientists.

Please note that this script is not functional; it serves only as an example.

Tip 1 : Concise but explanatory comments: Explain the purpose of a block of code, especially for important or complex steps.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Loading libraries

Tip 2 : Always comment on imported libraries, so that others know which dependencies are needed to make the code work.

```{r library, echo=FALSE}

# Load libraries required for analysis

library(ggplot2)  # For creating graphics
library(dplyr)    # For data manipulation
```

## Data loading and pre-processing

Tip 3 : When importing data, it's a good idea to add a comment explaining the source of the data and the import method. In addition, each data cleansing step should be accompanied by a comment explaining why it is necessary.

```{r}

# Import data
data <- read.csv("path/to/data.csv")

# Check the first few lines of data
head(data)

# Pre-processing data: cleaning up missing values
data_clean <- data %>%
  filter(!is.na(interesting_variable))

# Checking after cleaning
summary(data_clean)

```

## Data analysis

Tip 4 : Use explicit variable names and avoid abbreviations. Comment on analysis steps so others know what each line of code is trying to accomplish.

Tip 5: If you're working with functions, it's a good idea to specify the function's role, its inputs and outputs, and specify the type of each input and output.
It's not always necessary to comment so much on functions. But for complex ones, it's always easier if you want to go back over the code after you've done it.

Tip 6 : Checking input types : To avoid errors, it is often useful to check that a function's inputs are of the expected type (for example, by verifying that an argument is indeed a numerical vector).

Find out what's wrong with my function...

```{r}

# Function: calculer_moyenne
# Description: Computes the arithmetic mean of a numerical vector, ignoring missing values (`NA`).
#
# Inputs:
#   - x (numeric vector): A vector of numeric values for which the mean is calculated.
#
# Output:
#   - moyenne (numeric): A single numeric value representing the mean of the input vector.
#
# Notes:
#   - The input `x` must be a numeric vector. If `x` is not numeric, the function stops and raises an error.
#   - The input `x` must not be empty. If the vector has zero length, the function stops and raises an error.
#   - Missing values (`NA`) in the input vector are ignored during the calculation.
#   - The function uses the `mean()` function from base R with `na.rm = TRUE` to handle missing values.
calculer_moyenne <- function(x) {
  # Check that the argument is a numerical vector
  if(!is.numeric(x)) {
    stop("The argument must be a digital vector.")
  }
  
  # Check that the vector is not empty
  if (length(x) == 0) {
    stop("Error: the vector must not be empty.")
  }
  
  # Average calculation ignoring NA
  moyenne <- mean(x, na.rm = TRUE)
  
  # Return result
  return(moyenne)
}

#  Example of function use
data <- c(1, 2, 3, 4, 5, NA)  # Vector with missing values
resultat <- calculer_moyenne(data)

# Display result
resultat

```

Tip 7: Never put variables, function names... in a language other than English. It's annoying if you don't speak Italian, French, Russian or Chinese ....


## Viewing results

Tip 8 : Comment on each element of the visualization. For example, if you change colors or chart types, explain why these choices are made.

```{r}

# Create a simple graph
ggplot(data, aes(x = Interesting_variable)) +
  geom_histogram(binwidth = 1) +
  labs(title = "Distribution of the variable of interest",
       x = "Interesting variable",
       y = "Frequency")

```

```{r}

```

```{r}

```
